---
title: "Tidyverse Project DATA 607"
author: "Tyler Baker"
date: "10/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

I want to explain how to read in two csv and combine them the Tidy way. 

We first must find raw data.
For this example I was able to find two datasets. One is ticket prices for each NFL team, and the other is the popularity for each NFL team.

```{r}
nfl_ticket_prices_df<- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/nfl-ticket-prices/national-average.csv")

nfl_popular_teams_df <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/nfl-fandom/NFL_fandom_data-surveymonkey.csv")
```

Okay so now that we have uploaded the two datasets we must examine them. We  want to combine the datasets by their team name. 

To do this we must first cutoff the word `Tickets` from the ticket price dataframe.

```{r}
nfl_ticket_prices_df$Genre<- str_replace_all(nfl_ticket_prices_df$Genre, ".Tickets", "")
```

Then we must change the columnnames.

```{r}
colnames(nfl_ticket_prices_df) <- c("team", "ticket_price")
keep_columns<- c(1, 2, 8, 14, 20, 21, 22, 23)
nfl_popular_teams_df<- nfl_popular_teams_df[keep_columns]
colnames(nfl_popular_teams_df) <- c("team", "total_respondents", "total_democrat", "total_independent", "total_republican", "republican_percentage", "democrat_percentage", "independent_percentage")
nfl_popular_teams_df <- nfl_popular_teams_df[-c(1, 34),]
```

Now we can combine the two dataframes

```{r}
nfl_team_stats <- merge(nfl_popular_teams_df, nfl_ticket_prices_df, by = 'team')
```

That is how we can read in multiple csv's and combine them based on a shared column.